---
title: "Homework 3"
author: "Kunal Palawat and Colleen Yancey"
date: "2/4/2018"
output: 
  beamer_presentation: 
    colortheme: seahorse
    incremental: yes
    theme: Ilmenau
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Slide Title
Add your markdown text, etc. etc. for display on the screen, but remember, these are **slides** so we don't want too much text!

##Second Slide
- First incremental bullet point
- Second incremental bullet point
- Third incremental bullet point

##Third Slide
>- 1st incremental bullet point
>- 2nd incremental bullet point
>- 3rd incremental bullet point

$$
%this is a non-printing comment in LaTex
$$

##Slide Four
```{r, echo=FALSE}
library(ggplot2)
var1=runif(10)
var2=runif(10)
qplot(x=var1, y=var2)
```

##Slide Five
Colored Bullet Points

>- Collection Mode
>- \color{gray} Spatial and Temporal
>- \color{red} Taxonomic Bisa
>- \color{pink} Sampling
>- \color{black} more stuff

##
 \begin{picture}(320,250)
 \put(15,10){\includegraphics[height=6cm]
 {celtic.jpg}}
 \put(200,10){\includegraphics[height=6cm]
 {celtic.jpg}}
 \put(00,220){\begin{minipage}[t]{1\linewidth}
 {Choose a point on the unit circle. Connect it to the origin with a line of length one, and denote the angle between that line and the horizontal coordinate axis by $\theta$.}
 \end{minipage}}
 \end{picture}

##
Words

\bigskip
\bigskip
\bigskip
\bigskip

More words