---
title: 'Homework #4'
author: "Colleen Yancey"
date: "2/7/2018"
output: html_document
---

1. Suppose x= 1.1, a=2.2, and b=3.3. Assign each expression to the value of the varibale z and pring the value stored in z. 

```{r}
x <- 1.1
a <- 2.2
b <-3.3
#a
z <- x^(a^b)
print(z)
#b
z <-(x^a)^b
print(z)
#c
z <- 3*x^3 +2*x^2 + 1
print(z)

#d
floor((z %% floor(z))*10)



```

2. Using the rep and seq functions create the following vectors:
```{r}
x <- c(1:8, 7:1)
x

x <- rep(1:5, 1:5)
print(x)

x <- rep(5:1, 1:5)
print(x)
```

3. Create a vector oftwo random uniform numbers. In a spatial map, these can be interpreted as x and y coordinates that give the location of an individual (such as a marked forest tree in a plot that has been mapped). Using one of R's inverse trig functions, convert these number into polar coordinates.

```{r}
Cartesian <-runif(2)
print(Cartesian)

Polar <- vector(mode="numeric", length=2)
Polar[1] <- sqrt(Cartesian[1]^2 + Cartesian[2]^2)
Polar[2] <- atan(Cartesian[2]/Cartesian[1])
print(Polar)
```

4. Suppose that queue <- c("sheep", "fox", "owl", "ant") adn that queue represents the animals that are lined up to enter Noah's Ark, with the sheep at the front fo the line. Using R expressionsm update the queue.
```{r}
queue <- c("sheep", "fox", "owl", "ant")

#the serpent arrives
queue <- c(queue, "serpent")
print(queue)

# the sheep enters the ark
queue <- (queue[-1])
print(queue)

# the donkey arrives and talks his way to the front of the line
queue <- c("donkey", queue)
print(queue)

# the serpent gets impatient and leave
queue <- queue[-length(queue)]
print(queue)

#the owl gets bored and leaves
queue <-queue[queue !="owl"]
print(queue)

#the aphid arrives and the ant inviees him to cut in line
queue <-c(queue[-length(queue)],c("aphid", "ant"))
print(queue)
          
#Finally determine the position of aphid in line
which(queue=="aphid")


```

5. Use R to create a vector of all the integers from 1 to 100 that are not divisible by 2,3,or 7. 

```{r}
z <- seq(1,100)
z <- z[z%%2 !=0 & z%%3 !=0 & z%%7 !=0]
print(z)
```

6. Create a vector z of 1000 random uniform numbers.
a) create a vector that contains 3 numbers, the proportion of the numbers in z that are less than 0.1, greater than ,9, and between 0.45 and .55.
b) making successive copies of z, transform you vector of uniform numbers in the following various ways:
c) for each case, calculate your vector 3 number to get new proportions
```{r}
z <- runif(1000)
Propvector <- c(mean(z<.10), mean(z>.90), mean(z>.45 & z<.55))
print(Propvector)

#logbase10 of z
z <- log10(z)
Propvector <- c(mean(z<.10), mean(z>.90), mean(z>.45 & z<.55))
print(Propvector)

# z^2
z <-z^2
Propvector <- c(mean(z<.10), mean(z>.90), mean(z>.45 & z<.55))
print(Propvector)

#e^2
z <- exp(z)
Propvector <- c(mean(z<.10), mean(z>.90), mean(z>.45 & z<.55))
print(Propvector)

# sqrt(z)
z <- sqrt(z)
Propvector <- c(mean(z<.10), mean(z>.90), mean(z>.45 & z<.55))
print(Propvector)
```
d) Typset the formulas from R markdown (with $$ brackets)

$$ log_{10}(z) $$
$$ z^2 $$
$$ e^2 $$
$$ \sqrt{z} $$